The \emph{FThresholds} package for \emph{Macaulay2}

### 2019-06-05 Fsing/FThresholdsPaper/FThresholds.tex
minor rewording in the first page of the paper

\begin{abstract}
   This note describes the functionality implemented in the \emph{Macaulay2} package \emph{FThresholds}.
   This package is designed to compute and estimate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of regularity conditions in positive characteristic commutative algebra.
\end{abstract}

@@

This paper describes the \emph{Macaulay2} \cite{M2} package \emph{FThresholds}, which provides tools for computing certain fundamental invariants arising in positive characteristic commutative algebra, namely, \emph{$F$-pure thresholds}, \emph{$F$-thresholds}, and \emph{$F$-jumping exponents}.
Recall that a ring $R$ of prime characteristic $p>0$ is said to be \emph{$F$-pure} if the Frobenius morphism $F \: R \to R$ sending an element to its $p^\text{th}$ power is a pure morphism (under geometric hypotheses, this is equivalent to the condition that the Frobenius morphism is split).
The notion of $F$-purity first appeared in the work \cite{HochsterRobertsFrobeniusLocalCohomology}  of Hochster and Roberts to study local cohomology \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities in  \cite{FedderFPureRat}, and was used globally to study properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.

After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of the Frobenius endomorphism to measure regularity conditions proliferated, and based on a strong connection discovered between $F$-pure and \emph{log canonical} singularities \cite{HaraWatanabeFRegFPure}, the notion of $F$-purity was generalized to pairs $(R, f^t)$, where $f$ is an element of $R$, and $t$ is a nonnegative real number considered a formal exponent.

>>>>

\begin{abstract}
   This note describes the functionality implemented in the \emph{Macaulay2} package \emph{FThresholds}.
   This package is designed to compute and estimate $F$-pure thresholds, more general $F$-thresholds, and related numerical invariants arising in the study of singularities in positive characteristic commutative algebra.
\end{abstract}

@@

This paper describes the \emph{Macaulay2} \cite{M2} package \emph{FThresholds}, which provides tools for computing certain fundamental invariants arising in positive characteristic commutative algebra, namely, \emph{$F$-pure thresholds}, \emph{$F$-thresholds}, and \emph{$F$-jumping exponents}.
Recall that a ring $R$ of prime characteristic $p>0$ is said to be \emph{$F$-pure} if the Frobenius morphism $F \: R \to R$ sending an element to its $p^\text{th}$ power is a pure morphism (under geometric hypotheses, this is equivalent to the condition that the Frobenius morphism is split).  Regular rings are always $F$-pure, but not conversely.
The notion of $F$-purity first appeared in the work \cite{HochsterRobertsFrobeniusLocalCohomology}  of Hochster and Roberts to study local cohomology \cite{HochsterRobertsFrobeniusLocalCohomology}, was compared with rational singularities in  \cite{FedderFPureRat}, and was used globally to study properties of Schubert varieties in \cite{MehtaRamanathanFrobeniusSplittingAndCohomologyVanishing}.

After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of the Frobenius endomorphism to measure singularities proliferated, and based on a strong connection discovered between $F$-pure and \emph{log canonical} singularities \cite{HaraWatanabeFRegFPure}, the notion of $F$-purity was generalized to pairs $(R, f^t)$, where $f$ is an element of $R$, and $t$ is a nonnegative real number considered a formal exponent.
